### 2022-05-05 manuscript.Rmd
Improve figure placement

# Global chunk options
knitr::opts_chunk$set(
  include = FALSE,
  message = FALSE,
  fig.height = 10,
  fig.width = 7.5,
  out.width = "100%",
  warning = FALSE
)

>>>>

# Global chunk options
knitr::opts_chunk$set(
  include = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.height = 10,
  fig.pos = "tp",
  fig.width = 7.5,
  out.width = "100%",
  warning = FALSE
)
